E coli WT General Read Sequence Figure Generation

### 2022-05-31 R/EcoliWTDeaminationAnchoredExcisionSiteDataGeneration.rmd
Added E coli notebooks

---
title: "Arabidopsis Deamination Anchored Excision Site Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 10
cellType = "Arabidopsis"
CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
minReadLength = 24; maxReadLength = 30

>>>>

---
title: "E coli WT Deamination Anchored Excision Site Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 10
cellType = "E_coli_WT"
CPDTimepoints = list(`5min` = NULL)
minReadLength = 11; maxReadLength = 13

### 2022-05-31 R/EcoliWTDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added E coli notebooks

---
title: "Arabidopsis Deamination Anchored Excision Site Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

>>>>

---
title: "E coli WT Deamination Anchored Excision Site Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

### 2022-05-31 R/EcoliWTDeaminationSequenceAndPositionDataGeneration.rmd
Added E coli notebooks

---
title: "Arabidopsis Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 0
cellType = "Arabidopsis"
CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
minReadLength = 24; maxReadLength = 30

@@

```{r generate_and_write_mismatch_frequency_z-scores}
# Don't forget to subset by C>T mismatches!
CPDMMFreqZScores = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) {
    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset)
  }
))

>>>>

---
title: "E coli WT Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 0
cellType = "E_coli_WT"
CPDTimepoints = list(`5min` = NULL)
minReadLength = 11; maxReadLength = 13

@@

```{r generate_and_write_mismatch_frequency_z-scores}
# Don't forget to subset by C>T mismatches!
CPDMMFreqZScores = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) {
    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset, noisePositions = 5)
  }
))

### 2022-05-31 R/EcoliWTDeaminationSequenceAndPositionFigureGeneration.rmd
Added E coli notebooks

---
title: "Arabidopsis Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

cellType = "Arabidopsis"
CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
minReadLength = 24; maxReadLength = 30

>>>>

---
title: "E coli WT Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

cellType = "E_coli_WT"
CPDTimepoints = list(`5min` = NULL)
minReadLength = 11; maxReadLength = 13

### 2022-05-31 R/EcoliWTGeneralReadSequenceDataGeneration.rmd
Added E coli notebooks

---
title: "CS-B General Read Sequence Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

expansionOffset = 10
cellType = "CS-B"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

>>>>

---
title: "E coli WT General Read Sequence Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

expansionOffset = 10
cellType = "E_coli_WT"
CPDTimepoints = list(`5min` = NULL)
minReadLength = 11; maxReadLength = 13

### 2022-05-31 R/EcoliWTGeneralReadSequenceFigureGeneration.rmd
Added E coli notebooks

---
title: "Arabidopsis General Read Sequence Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

>>>>

---
title: "E coli WT General Read Sequence Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---
